---
title: "Build App Databases"
author: "David Ory"
output: 
   html_document:
      theme: cosmo
      toc: yes
---

## Administration

#### Purpose
For the Innovations Conference App, I've created a set of working databases that I edit in Excel/text editor.  These are in `working` --> `sessions.csv`, `speakers.csv`, and `exhibitors.csv`.  This script consumes those databases and does the following:

1.  Checks that each speaker identified in `sessions.csv` is a member of `speakers.csv`.
2.  Replaces the intuitive speaker ID with a unique integer in both `speakers.csv` and `sessions.csv`.
3.  Replaces the somewhat intuitive session ID with a unique integer in `sessions.csv`.
4.  Writes out refreshed databases to the `production` directory.

#### Outputs
1.  A set of updated databases written to the `production` directory. 
2.  A list of speaker names that are in the `session.csv` database but not the `speakers.csv` database.

#### _TODO_
1.  More or less everything, start with Step 2
2.  Clean up Step 1

## Procedure

#### Overhead
```{r overhead, results = 'hide'}
library(knitr)
library(reshape2)
suppressMessages(library(dplyr))
library(stringr)
```

```{r config, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

#### Remote I/O
```{r remote-io}
INPUT_SESSIONS   = "../working/sessions.csv"
INPUT_SPEAKERS   = "../working/speakers.csv"
INPUT_EXHIBITORS = "../working/exhibitors.csv"

OUTPUT_SESSIONS   = "../production/sessions.csv"
OUTPUT_SPEAKERS   = "../production/speakers.csv"
OUTPUT_EXHIBITORS = "../production/exhibitors.csv"
```

#### Data reads
```{r data-reads}
input_sessions   <- read.table(file = INPUT_SESSIONS,   header = TRUE, sep = ",", stringsAsFactors = FALSE)
input_speakers   <- read.table(file = INPUT_SPEAKERS,   header = TRUE, sep = ",", stringsAsFactors = FALSE)
input_exhibitors <- read.table(file = INPUT_EXHIBITORS, header = TRUE, sep = ",", stringsAsFactors = FALSE) 

```

#### Step 1: Check for integrity of session database speaker ID list
```{r speaker-check}
# first bit: get a unique list of speakers from the sessions database
speaker_list <- input_sessions %>%
  select(Speaker.IDs)

speaker_variables = c("speaker_01", "speaker_02", "speaker_03", "speaker_04", "speaker_05", 
                      "speaker_06", "speaker_07", "speaker_08", "speaker_09", "speaker_10", 
                      "speaker_11", "speaker_12", "speaker_13", "speaker_14", "speaker_15")

speaker_list <- cbind(speaker_list, colsplit(speaker_list$Speaker.IDs, ",", speaker_variables))

speaker_condensed <- speaker_list %>%
  select(speaker = speaker_01)

for (i in 2:length(speaker_variables)) {
  
  working <- speaker_list[][speaker_variables[i]]
  colnames(working) <- c("speaker")
  
  speaker_condensed <- rbind(speaker_condensed, working)
  
}

speaker_condensed <- speaker_condensed %>%
  filter(is.na(speaker) == FALSE) %>%
  filter(str_length(speaker) > 1) %>%
  group_by(speaker) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  select(speaker) %>%
  mutate(speaker = str_trim(speaker))

# second bit: compare the unique list to the speaker database
speaker_working <- input_speakers %>%
  select(speaker = Speaker.ID, first_name = First.Name..required., last_name = Last.Name..required.) %>%
  mutate(speaker = str_trim(speaker))

speaker_compare <- left_join(speaker_condensed, speaker_working, by = c("speaker"))

speaker_errors <- speaker_compare %>%
  filter(is.na(first_name))

speaker_errors
  
remove(speaker_compare, speaker_condensed, speaker_list, speaker_working, working)  

```


